---
title: "T-SNE-predict"
author: '610811101'
date: "2020/11/14"
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

https://lvdmaaten.github.io/tsne/


**Once I have a t-SNE map, how can I embed incoming test points in that map?**

>t-SNE learns a non-parametric mapping, which means that it does not learn an explicit function that maps data from the input space to the map. Therefore, it is not possible to embed test points in an existing map (although you could re-run t-SNE on the full dataset). A potential approach to deal with this would be to train a multivariate regressor to predict the map location from the input data. Alternatively, you could also make such a regressor minimize the t-SNE loss directly, which is what I did in this paper.
 
 

```{r include=FALSE}
library(highcharter)
library(tidyverse)
library(tidytext)
library(Rtsne)
library(magrittr)
```




```{r}
finaldata9815 <- read.csv("G:/我的雲端硬碟/meeting/finaldata9815.csv")

colname <- c("IC","OM","TDL","DP","MBA","RDA","REA","CEA","CBA","TA","beta","sigma","size","S.P.500.return")
finaldata9815 <- finaldata9815[,c(colname,"LTR.rating.categories")]
finaldata9815 <- finaldata9815[!(is.na(finaldata9815) %>% rowSums()),]

data_out <- read.csv("G:/我的雲端硬碟/meeting/data_out.csv")
data_in <- read.csv("G:/我的雲端硬碟/meeting/data_in.csv")

mnist <- snedata::download_mnist()

```






# function  


```{r}
center <- function(x){
  x_mean <- matrix(colMeans(x),nrow = nrow(x),ncol = ncol(x),byrow = T)
  x-x_mean
}

train_tsne <- function(data){
  ## the function is use by myself , so it has not check anything
  pca <- prcomp(data)
  Y_init <- as.matrix(pca$x[,1:2])
  
  tsne <- Rtsne(data,check_duplicates = F,Y_init = Y_init)
  tsne[["Y_init"]] <- Y_init
  tsne[["pca_coef"]] <- as.matrix(pca$rotation[,1:2])
  tsne[["center"]] <- pca$center
  class(tsne) <- "TSNE"
  tsne
}

# predict_tsne <- function(TSNE,train,test){
#   ## the function is use by myself , so it has not check anything 
#   train_pca <- prcomp(train)
#   test_mean <- matrix(colMeans(train),nrow = nrow(test),ncol = ncol(train))
#   train_pca_value <- as.matrix(train_pca$x[,1:2])
#   test_pca_value <- as.matrix(test-test_mean) %*% as.matrix(train_pca$rotation[,1:2])
#   test_predict <- matrix(nrow = nrow(test),ncol = 2) %>%
#     as.data.frame() %>%
#     `names<-`(c("x","y"))
#   for(i in 1:nrow(test)){
#     
#   }
# }

predict_tsne <- function(TSNE,test,k = 5){
  ## the function is use by myself , so it has not check anything 
  if(class(TSNE)!="TSNE"){
    stop("class is not TSNE")
  }
  test_mean <- matrix(TSNE$center,nrow = nrow(test),ncol = ncol(test),byrow = T)
  
  RS <- TSNE$Y-TSNE$Y_init
  
  test_pca_value <- as.matrix(test-test_mean) %*% TSNE$pca_coef
  
  test_predict <- matrix(nrow = nrow(test),ncol = 2) %>%
    as.data.frame() %>%
    `names<-`(c("x","y"))
  
  for(i in 1:nrow(test)){
    test_dist_order <- (TSNE$Y_init-matrix(test_pca_value[i,],ncol = 2,nrow = nrow(TSNE$Y_init),byrow = T))^2 %>% rowSums() %>% order()
    index <- test_dist_order[1:k]
    move <- RS[index,] %>% colMeans()
    test_predict[i,] <- test_pca_value[i,]+move
  }
  test_predict
}
```




# iris  


```{r}
set.seed(610811101)
iris_index <- sample(1:nrow(iris),size = floor(0.8*nrow(iris)))
iris_train <- iris[iris_index,]
iris_test <- iris[-iris_index,]
set.seed(610811101)
iris_tsne <- train_tsne(iris_train[,1:4])
iris_pred <- predict_tsne(TSNE = iris_tsne,test = iris_test[,1:4],k = 3) %>%
  as.data.frame() %>%
  cbind(iris_test$Species) %>%
  `names<-`(c("x","y","Species"))


```


```{r}
iris_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(iris_train$Species) %>%
  `names<-`(c("x","y","Species")) %>%
  hchart("scatter", hcaes(x=x,y=y,group = Species)) %>%
  hc_title(text ="iris_train") 


```

## 使用MDS predict

```{r}
  
hchart(iris_pred,"scatter", hcaes(x=x,y=y,group = Species)) %>%
  hc_title(text ="iris_pred") 
```

```{r}
  
iris_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(iris_train$Species) %>%
  `names<-`(c("x","y","Species")) %>%
  rbind(iris_pred) %>%
  hchart("scatter", hcaes(x=x,y=y,group = Species)) %>%
  hc_title(text ="iris_all") 

```

## 用Multivariate multiple regression predict  

```{r}
iris_lm <- iris_tsne %$%
  Y %>%
  as.data.frame() %>%
  `names<-`(c("x","y"))  %>%
  cbind(iris_train[,1:4]) %>%
  lm(cbind(x,y)~.,data = .)    
    
iris_pred_2 <- predict(iris_lm,iris_test[,1:4]) %>%
  as.data.frame() %>%
  cbind(iris_test$Species) %>%
  `names<-`(c("x","y","Species")) 

  hchart(iris_pred_2,"scatter", hcaes(x=x,y=y,group = Species)) %>%
  hc_title(text ="iris_pred")
```


```{r}

iris_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(iris_train$Species) %>%
  `names<-`(c("x","y","Species")) %>%
  rbind(iris_pred_2) %>%
  hchart("scatter", hcaes(x=x,y=y,group = Species)) %>%
  hc_title(text ="iris_all") 
```



# finaldata9815  





```{r}
set.seed(610811101)
finaldata_index <- sample(1:nrow(finaldata9815),size = floor(0.8*nrow(finaldata9815)))
finaldata_train <- finaldata9815[finaldata_index,]
finaldata_test <- finaldata9815[-finaldata_index,]
set.seed(610811101)
finaldata_tsne <- train_tsne(finaldata_train[,1:14])
finaldata_pred <- predict_tsne(TSNE = finaldata_tsne,test = finaldata_test[,1:14],k = 3) %>%
  as.data.frame() %>%
  cbind(finaldata_test$LTR.rating.categories) %>%
  `names<-`(c("x","y","LTR"))


```


```{r}
finaldata_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(finaldata_train$LTR.rating.categories) %>%
  `names<-`(c("x","y","LTR")) %>%
  hchart("scatter", hcaes(x=x,y=y,group = LTR)) %>%
  hc_title(text ="finaldata_train") 
  

```

## 使用MDS predict   

```{r}

hchart(finaldata_pred,"scatter", hcaes(x=x,y=y,group = LTR)) %>%
  hc_title(text ="finaldata_pred") 



```


```{r}
finaldata_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(finaldata_train$LTR.rating.categories) %>%
  `names<-`(c("x","y","LTR")) %>%
  rbind(finaldata_pred) %>%
  hchart("scatter", hcaes(x=x,y=y,group = LTR)) %>%
  hc_title(text ="finaldata_all") 


```


## 用Multivariate multiple regression predict  


```{r}
finaldata_lm <- finaldata_tsne %$%
  Y %>%
  as.data.frame() %>%
  `names<-`(c("x","y"))  %>%
  cbind(finaldata_train[,1:14]) %>%
  lm(cbind(x,y)~.,data = .)    
    
finaldata_pred_2 <- predict(finaldata_lm,finaldata_test[,1:14]) %>%
  as.data.frame() %>%
  cbind(finaldata_test$LTR.rating.categories) %>%
  `names<-`(c("x","y","LTR")) 

hchart(finaldata_pred_2,"scatter", hcaes(x=x,y=y,group = LTR)) %>%
  hc_title(text ="finaldata_pred") 
```



```{r}
finaldata_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(finaldata_train$LTR.rating.categories) %>%
  `names<-`(c("x","y","LTR")) %>%
  rbind(finaldata_pred_2) %>%
  hchart("scatter", hcaes(x=x,y=y,group = LTR)) %>%
  hc_title(text ="finaldata_all") 
```


# data_in  




```{r}

set.seed(610811101)
LGD_tsne <- train_tsne(data_in[,4:15])
LGD_pred <- predict_tsne(TSNE = LGD_tsne,test = data_out[,4:15],k = 3) %>%
  as.data.frame() %>%
  cbind(data_out$LGD) %>%
  `names<-`(c("x","y","LGD"))


```


```{r}
LGD_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(data_in$LGD) %>%
  `names<-`(c("x","y","LGD")) %>%
  hchart("scatter", hcaes(x=x,y=y,color = LGD)) %>%
  hc_title(text ="LGD_train") 
  
```

## 使用MDS predict  

```{r}

hchart(LGD_pred,"scatter", hcaes(x=x,y=y,color = LGD)) %>%
  hc_title(text ="LGD_pred") 
```


```{r}
LGD_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(data_in$LGD) %>%
  `names<-`(c("x","y","LGD")) %>%
  rbind(LGD_pred) %>%
  hchart("scatter", hcaes(x=x,y=y,color = LGD)) %>%
  hc_title(text ="LGD_all") 


```

## 用Multivariate multiple regression predict  

```{r}
LGD_lm <- LGD_tsne %$%
  Y %>%
  as.data.frame() %>%
  `names<-`(c("x","y"))  %>%
  cbind(data_in[,4:15]) %>%
  lm(cbind(x,y)~.,data = .)    
    
LGD_pred_2 <- predict(LGD_lm,data_out[,4:15]) %>%
  as.data.frame() %>%
  cbind(data_out$LGD) %>%
  `names<-`(c("x","y","LGD")) 

hchart(LGD_pred_2,"scatter", hcaes(x=x,y=y,color = LGD)) %>%
  hc_title(text ="LGD_pred") 
```


```{r}
LGD_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(data_in$LGD) %>%
  `names<-`(c("x","y","LGD")) %>%
  rbind(LGD_pred_2) %>%
  hchart("scatter", hcaes(x=x,y=y,color = LGD)) %>%
  hc_title(text ="LGD_all") 
```

# mnist   


```{r}
set.seed(610811101)
mnist_index <- sample(1:nrow(mnist),size = floor(0.8*nrow(mnist)))
mnist_train <- mnist[mnist_index,]
mnist_test <- mnist[-mnist_index,]
set.seed(610811101)
mnist_tsne <- train_tsne(mnist_train[,1:784])
mnist_pred <- predict_tsne(TSNE = mnist_tsne,test = mnist_test[,1:784])%>%
  as.data.frame() %>%
  cbind(mnist_test$Label) %>%
  `names<-`(c("x","y","Label"))


```



```{r}



mnist_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(mnist_train$Label) %>%
  `names<-`(c("x","y","Label")) %>%
  hchart("scatter", hcaes(x=x,y=y,group = Label)) %>%
  hc_title(text ="mnist_train") 
  

```

## 使用MDS predict  

```{r}

hchart(mnist_pred,"scatter", hcaes(x=x,y=y,group = Label)) %>%
  hc_title(text ="mnist_pred") 


```

```{r}

mnist_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(mnist_train$Label) %>%
  `names<-`(c("x","y","Label")) %>%
  rbind(mnist_pred) %>%
  hchart("scatter", hcaes(x=x,y=y,group = Label)) %>%
  hc_title(text ="mnist_all") 

```

## 用Multivariate multiple regression predict  


```{r}
mnist_lm <- mnist_tsne %$%
  Y %>%
  as.data.frame() %>%
  `names<-`(c("x","y"))  %>%
  cbind(mnist_train[,1:784]) %>%
  lm(cbind(x,y)~.,data = .)    
    
mnist_pred_2 <- predict(mnist_lm,mnist_test[,1:784]) %>%
  as.data.frame() %>%
  cbind(mnist_test$Label) %>%
  `names<-`(c("x","y","Label")) 

hchart(mnist_pred_2,"scatter", hcaes(x=x,y=y,group = Label)) %>%
  hc_title(text ="mnist_pred") 
```


```{r}
mnist_tsne %$%
  Y %>%
  as.data.frame() %>%
  cbind(mnist_train$Label) %>%
  `names<-`(c("x","y","Label")) %>%
  rbind(mnist_pred_2) %>%
  hchart("scatter", hcaes(x=x,y=y,group = Label)) %>%
  hc_title(text ="mnist_all") 
```

