---
title: "weight-T-SNE"
author: '610811101'
date: "2021/1/26"
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

```{r include=FALSE}
library(highcharter)
library(tidyverse)
library(tidytext)
library(Rtsne)
library(wtsne)
library(magrittr)
library(xgboost)
```

```{r}
# data
mnist <- snedata::download_mnist()
fashion_mnist <- snedata::download_fashion_mnist()
```

```{r}

weight_index <- function(data,pred,seed = NULL,N = NROW(data)*2){
  lottery <- sapply(1:N, function(x){
    if(!is.null(seed)){
      set.seed(seed+x)
    }
    sample(1:NROW(data),2)
  }) %>% t()
  data_dist <- (data[lottery[,1],]-data[lottery[,2],])^2 %>% rowSums()
  if(!is.vector(pred)){
    pred_dist <- (pred[lottery[,1],]-pred[lottery[,2],])^2 %>% rowSums()
  }else{
    pred_dist <- (pred[lottery[,1]]-pred[lottery[,2]])^2 
  }
  
  proportion <- data.frame("data" = data_dist,"pred" = pred_dist) %>% sqrt()
  allproportion <- colSums(proportion)
  allproportion <- allproportion[1]/allproportion[2]
  
  return(list("proportion"=proportion,"allproportion"=allproportion))
}


```

```{r}
weight_by_index <- function(now_index,want_index,data,pred){
  mul <- now_index/want_index
  if(is.vector(pred)){
    c(rep(1,ncol(data)),mul)
  }else{
    c(rep(1,ncol(data)),rep(mul,ncol(pred)))
  }
}
```

# iris

```{r}
index <- sample(1:nrow(iris),50)
xgb_iris <- xgb.DMatrix(data=as.matrix(iris[index,-5]),label=as.numeric(iris[index,5])-1)
iris_num_class <- length(levels(iris$Species))
xgb_fit <- xgboost(data = xgb_iris, 
eta = 0.5,
max_depth = 10, 
nround=25, 
subsample = 0.7,
colsample_bytree = 0.7,
objective = "multi:softprob",
num_class= iris_num_class,
verbose = 0
)
label <- predict(xgb_fit,as.matrix(iris[-index,-5]),reshape=T) %>%
  as.data.frame() %>%
  `colnames<-`(levels(iris$Species))
```

## find good N

### n = 100, N = 10

```{r}
weight_index_iris <- rep(NA,1000)
for(i in 1:1000){
  weight_index_iris[i] <- weight_index(iris[-index,1:4],label,N = 10)$allproportion
}
plot(density(weight_index_iris))

```

### n = 100 , N = 50

```{r}
weight_index_iris <- rep(NA,1000)
for(i in 1:1000){
  weight_index_iris[i] <- weight_index(iris[-index,1:4],label,N = 50)$allproportion
}
plot(density(weight_index_iris))
```

### n = 100 , N = 100

```{r}
weight_index_iris <- rep(NA,1000)
for(i in 1:1000){
  weight_index_iris[i] <- weight_index(iris[-index,1:4],label,N = 100)$allproportion
}
plot(density(weight_index_iris))
```

### n = 100 , N = 200

```{r}
weight_index_iris <- rep(NA,1000)
for(i in 1:1000){
  weight_index_iris[i] <- weight_index(iris[-index,1:4],label,N = 200)$allproportion
}
plot(density(weight_index_iris))
```

## find good weight

目前指標

```{r}
(iris_index <- weight_index(iris[-index,1:4],label,N = 200)$allproportion)
```

### index = 8 

```{r}
w <- weight_by_index(iris_index,8,iris[-index,1:4],label)
set.seed(610811101)
iris_tsne_2 <- cbind(iris[-index,-5],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(iris[-index,ncol(iris)]) %>% 
  `names<-`(c("x","y","group"))

hchart(iris_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="iris") 
```

### index = 5

```{r}
w <- weight_by_index(iris_index,5,iris[-index,1:4],label)
set.seed(610811101)
iris_tsne_2 <- cbind(iris[-index,-5],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(iris[-index,ncol(iris)]) %>% 
  `names<-`(c("x","y","group"))

hchart(iris_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="iris") 
```

### index = 2

```{r}
w <- weight_by_index(iris_index,2,iris[-index,1:4],label)
set.seed(610811101)
iris_tsne_2 <- cbind(iris[-index,-5],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(iris[-index,ncol(iris)]) %>% 
  `names<-`(c("x","y","group"))

hchart(iris_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="iris") 
```

### index = 1

```{r}
w <- weight_by_index(iris_index,1,iris[-index,1:4],label)
set.seed(610811101)
iris_tsne_2 <- cbind(iris[-index,-5],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(iris[-index,ncol(iris)]) %>% 
  `names<-`(c("x","y","group"))

hchart(iris_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="iris") 
```

### index = 0.5

```{r}
w <- weight_by_index(iris_index,0.5,iris[-index,1:4],label)
set.seed(610811101)
iris_tsne_2 <- cbind(iris[-index,-5],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(iris[-index,ncol(iris)]) %>% 
  `names<-`(c("x","y","group"))

hchart(iris_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="iris") 
```

### index = 0.25

```{r}
w <- weight_by_index(iris_index,0.25,iris[-index,1:4],label)
set.seed(610811101)
iris_tsne_2 <- cbind(iris[-index,-5],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(iris[-index,ncol(iris)]) %>% 
  `names<-`(c("x","y","group"))

hchart(iris_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="iris") 
```

# mnist

```{r}
index <- sample(1:nrow(mnist),65000)
xgb_mnist <- xgb.DMatrix(data=as.matrix(mnist[index,1:784]),label=as.numeric(mnist[index,785])-1)
mnist_num_class <- length(levels(mnist$Label))
xgb_fit <- xgboost(data = xgb_mnist, 
eta = 0.5,
max_depth = 10, 
nround=25, 
subsample = 0.7,
colsample_bytree = 0.7,
objective = "multi:softprob",
num_class= mnist_num_class,
verbose = 0
)
label <- predict(xgb_fit,as.matrix(mnist[-index,1:784]),reshape=T) %>%
  as.data.frame() %>%
  `colnames<-`(levels(mnist$Label))
```

## find good N

### n = 5000, N = 500

```{r}
weight_index_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_mnist[i] <- weight_index(mnist[-index,1:784],label,N = 500)$allproportion
}
plot(density(weight_index_mnist))
```

### n = 5000, N = 2500

```{r}
weight_index_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_mnist[i] <- weight_index(mnist[-index,1:784],label,N = 2500)$allproportion
}
plot(density(weight_index_mnist))
```

### n = 5000, N = 5000

```{r}
weight_index_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_mnist[i] <- weight_index(mnist[-index,1:784],label,N = 5000)$allproportion
}
plot(density(weight_index_mnist))
```

### n = 5000, N = 10000

```{r}
weight_index_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_mnist[i] <- weight_index(mnist[-index,1:784],label,N = 10000)$allproportion
}
plot(density(weight_index_mnist))
```

## find good weight

目前指標

```{r}
(mnist_index <- weight_index(mnist[-index,1:784],label,N = 10000)$allproportion)
```



### index = 8

```{r}
w <- weight_by_index(mnist_index,8,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```

### index = 5

```{r}
w <- weight_by_index(mnist_index,5,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```

### index = 2

```{r}
w <- weight_by_index(mnist_index,2,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```

### index = 1

```{r}
w <- weight_by_index(mnist_index,1,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```

### index = 0.5

```{r}
w <- weight_by_index(mnist_index,0.5,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```

### index = 0.25

```{r}
w <- weight_by_index(mnist_index,0.25,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```




# mnist 2

有加pred的資訊和沒加差太少，這個方法不能跑。

```{r eval=FALSE, include=FALSE}
index <- sample(1:nrow(mnist),65000)
mnist$class <- as.numeric(mnist$Label) %% 3

xgb_mnist <- xgb.DMatrix(data=as.matrix(mnist[index,1:784]),label=mnist$class[index])
mnist_num_class <- length(unique(mnist$class))
xgb_fit <- xgboost(data = xgb_mnist, 
eta = 0.5,
max_depth = 10, 
nround=25, 
subsample = 0.7,
colsample_bytree = 0.7,
objective = "multi:softprob",
num_class= mnist_num_class,
verbose = 0
)
label <- predict(xgb_fit,as.matrix(mnist[-index,1:784]),reshape=T) %>%
  as.data.frame() %>%
  `colnames<-`(levels(mnist$class))
```





## find good N

### n = 5000, N = 500

```{r eval=FALSE, include=FALSE}
weight_index_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_mnist[i] <- weight_index(mnist[-index,1:784],label,N = 500)$allproportion
}
plot(density(weight_index_mnist))
```

### n = 5000, N = 2500

```{r eval=FALSE, include=FALSE}
weight_index_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_mnist[i] <- weight_index(mnist[-index,1:784],label,N = 2500)$allproportion
}
plot(density(weight_index_mnist))
```

### n = 5000, N = 5000

```{r eval=FALSE, include=FALSE}
weight_index_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_mnist[i] <- weight_index(mnist[-index,1:784],label,N = 5000)$allproportion
}
plot(density(weight_index_mnist))
```

### n = 5000, N = 10000

```{r eval=FALSE, include=FALSE}
weight_index_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_mnist[i] <- weight_index(mnist[-index,1:784],label,N = 10000)$allproportion
}
plot(density(weight_index_mnist))
```

## find good weight

目前指標

```{r eval=FALSE, include=FALSE}
(mnist_index <- weight_index(mnist[-index,1:784],label,N = 10000)$allproportion)
```



### index = 8

```{r eval=FALSE, include=FALSE}
w <- weight_by_index(mnist_index,8,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```

### index = 5

```{r eval=FALSE, include=FALSE}
w <- weight_by_index(mnist_index,5,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```

### index = 2

```{r eval=FALSE, include=FALSE}
w <- weight_by_index(mnist_index,2,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```

### index = 1

```{r eval=FALSE, include=FALSE}
w <- weight_by_index(mnist_index,1,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```

### index = 0.5

```{r eval=FALSE, include=FALSE}
w <- weight_by_index(mnist_index,0.5,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```

### index = 0.25

```{r eval=FALSE, include=FALSE}
w <- weight_by_index(mnist_index,0.25,mnist[-index,1:784],label)
set.seed(610811101)
mnist_tsne_2 <- cbind(mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="mnist") 
```


# fashion_mnist

```{r}
index <- sample(1:nrow(fashion_mnist),65000)
xgb_fashion_mnist <- xgb.DMatrix(data=as.matrix(fashion_mnist[index,1:784]),label=as.numeric(fashion_mnist$Label[index])-1)
fashion_mnist_num_class <- length(levels(fashion_mnist$Label))
xgb_fit <- xgboost(data = xgb_fashion_mnist, 
eta = 0.5,
max_depth = 10, 
nround=25, 
subsample = 0.7,
colsample_bytree = 0.7,
objective = "multi:softprob",
num_class= fashion_mnist_num_class,
verbose = 0
)
label <- predict(xgb_fit,as.matrix(fashion_mnist[-index,1:784]),reshape=T) %>%
  as.data.frame() %>%
  `colnames<-`(levels(fashion_mnist$Label))
```

## find good N

### n = 5000, N = 500

```{r}
weight_index_fashion_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_fashion_mnist[i] <- weight_index(fashion_mnist[-index,1:784],label,N = 500)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 5000, N = 2500

```{r}
weight_index_fashion_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_fashion_mnist[i] <- weight_index(fashion_mnist[-index,1:784],label,N = 2500)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 5000, N = 5000

```{r}
weight_index_fashion_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_fashion_mnist[i] <- weight_index(fashion_mnist[-index,1:784],label,N = 5000)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 5000, N = 10000

```{r}
weight_index_fashion_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_fashion_mnist[i] <- weight_index(fashion_mnist[-index,1:784],label,N = 10000)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

## find good weight

目前指標

```{r}
(fashion_mnist_index <- weight_index(fashion_mnist[-index,1:784],label,N = 10000)$allproportion)
```


### index = 8

```{r}
w <- weight_by_index(fashion_mnist_index,8,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```

### index = 5

```{r}
w <- weight_by_index(fashion_mnist_index,5,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```

### index = 2

```{r}
w <- weight_by_index(fashion_mnist_index,2,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```

### index = 1

```{r}
w <- weight_by_index(fashion_mnist_index,1,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```

### index = 0.5

```{r}
w <- weight_by_index(fashion_mnist_index,0.5,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```

### index = 0.25

```{r}
w <- weight_by_index(fashion_mnist_index,0.25,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$Label[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```




# fashion_mnist 2

```{r}
index <- sample(1:nrow(fashion_mnist),65000)
fashion_mnist$class <- 0
fashion_mnist$class[fashion_mnist$Description %in% c("Coat","Shirt","Pullover","T-shirt/top")] <- "top"
fashion_mnist$class[fashion_mnist$Description %in% c("Dress","Trouser")] <- "Dress/Trouser"
fashion_mnist$class[fashion_mnist$Description %in% c("Ankle boot","Sneaker","Sandal","Bag")] <- "Not clothes"
fashion_mnist$class <- as.factor(fashion_mnist$class)
xgb_fashion_mnist <- xgb.DMatrix(data=as.matrix(fashion_mnist[index,1:784]),label=as.numeric(fashion_mnist$class[index])-1)
fashion_mnist_num_class <- length(levels(fashion_mnist$class))
xgb_fit <- xgboost(data = xgb_fashion_mnist, 
eta = 0.5,
max_depth = 10, 
nround=25, 
subsample = 0.7,
colsample_bytree = 0.7,
objective = "multi:softprob",
num_class= fashion_mnist_num_class,
verbose = 0
)
label <- predict(xgb_fit,as.matrix(fashion_mnist[-index,1:784]),reshape=T) %>%
  as.data.frame() %>%
  `colnames<-`(levels(fashion_mnist$class))
```





## find good N

### n = 5000, N = 500

```{r}
weight_index_fashion_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_fashion_mnist[i] <- weight_index(fashion_mnist[-index,1:784],label,N = 500)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 5000, N = 2500

```{r}
weight_index_fashion_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_fashion_mnist[i] <- weight_index(fashion_mnist[-index,1:784],label,N = 2500)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 5000, N = 5000

```{r}
weight_index_fashion_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_fashion_mnist[i] <- weight_index(fashion_mnist[-index,1:784],label,N = 5000)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 5000, N = 10000

```{r}
weight_index_fashion_mnist <- rep(NA,1000)
for(i in 1:1000){
  weight_index_fashion_mnist[i] <- weight_index(fashion_mnist[-index,1:784],label,N = 10000)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

## find good weight

目前指標

```{r}
(fashion_mnist_index <- weight_index(fashion_mnist[-index,1:784],label,N = 10000)$allproportion)
```



### index = 8

```{r}
w <- weight_by_index(fashion_mnist_index,8,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```

### index = 5

```{r}
w <- weight_by_index(fashion_mnist_index,5,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```

### index = 2

```{r}
w <- weight_by_index(fashion_mnist_index,2,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```

### index = 1

```{r}
w <- weight_by_index(fashion_mnist_index,1,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```

### index = 0.5

```{r}
w <- weight_by_index(fashion_mnist_index,0.5,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```

### index = 0.25

```{r}
w <- weight_by_index(fashion_mnist_index,0.25,fashion_mnist[-index,1:784],label)
set.seed(610811101)
fashion_mnist_tsne_2 <- cbind(fashion_mnist[-index,1:784],label) %>% 
  wtsne(check_duplicates = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(fashion_mnist$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(fashion_mnist_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="fashion_mnist") 
```



# swiss_roll

```{r}
swiss_roll <- snedata::swiss_roll(min_phi = 0,max_phi = 10*pi)
hchart(swiss_roll,"scatter",hcaes(x = x,y=y,color = color))
swiss_roll$class <- sqrt((swiss_roll$x)^2+(swiss_roll$y)^2) %/% (2*pi)

index <- sample(1:nrow(swiss_roll),0.6*nrow(swiss_roll))

hchart(swiss_roll,"scatter",hcaes(x = x,y=y,group = class))
swiss_roll$class <- as.factor(swiss_roll$class)

xgb_swiss_roll <- xgb.DMatrix(data=as.matrix(swiss_roll[index,1:3]),label=as.numeric(swiss_roll$class[index])-1)
swiss_roll_num_class <- length(levels(swiss_roll$class))
xgb_fit <- xgboost(data = xgb_swiss_roll, 
eta = 0.5,
max_depth = 10, 
nround=25, 
subsample = 0.7,
colsample_bytree = 0.7,
objective = "multi:softprob",
num_class= swiss_roll_num_class,
verbose = 0
)
label <- predict(xgb_fit,as.matrix(swiss_roll[-index,1:3]),reshape=T) %>%
  as.data.frame() %>%
  `colnames<-`(levels(swiss_roll$class))
```


## find good N

### n = 400, N = 40

```{r}
weight_index_swiss_roll <- rep(NA,1000)
for(i in 1:1000){
  weight_index_swiss_roll[i] <- weight_index(swiss_roll[-index,1:3],label,N = 40)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 400, N = 200

```{r}
weight_index_swiss_roll <- rep(NA,1000)
for(i in 1:1000){
  weight_index_swiss_roll[i] <- weight_index(swiss_roll[-index,1:3],label,N = 200)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 400, N = 400

```{r}
weight_index_swiss_roll <- rep(NA,1000)
for(i in 1:1000){
  weight_index_swiss_roll[i] <- weight_index(swiss_roll[-index,1:3],label,N = 400)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 400, N = 800

```{r}
weight_index_swiss_roll <- rep(NA,1000)
for(i in 1:1000){
  weight_index_swiss_roll[i] <- weight_index(swiss_roll[-index,1:3],label,N = 800)$allproportion
}
plot(density(weight_index_fashion_mnist))
```



## find good weight

目前指標

```{r}
(swiss_roll_index <- weight_index(swiss_roll[-index,1:3],label,N = 800)$allproportion)
```


### index = 8 

```{r}
w <- weight_by_index(swiss_roll_index,8,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```


### index = 5 

```{r}
w <- weight_by_index(swiss_roll_index,5,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```

### index = 2 

```{r}
w <- weight_by_index(swiss_roll_index,2,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```

### index = 1 

```{r}
w <- weight_by_index(swiss_roll_index,1,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```

### index = 0.5 

```{r}
w <- weight_by_index(swiss_roll_index,0.5,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```

### index = 0.25 

```{r}
w <- weight_by_index(swiss_roll_index,0.25,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```


# swiss_roll 2

```{r}
swiss_roll <- snedata::swiss_roll(min_phi = 0,max_phi = 10*pi)
hchart(swiss_roll,"scatter",hcaes(x = x,y=y,color = color))
swiss_roll$class <- (sqrt((swiss_roll$x)^2+(swiss_roll$y)^2) %/% (2*pi)) %% 2

index <- sample(1:nrow(swiss_roll),0.6*nrow(swiss_roll))

hchart(swiss_roll,"scatter",hcaes(x = x,y=y,group = class))
swiss_roll$class <- as.factor(swiss_roll$class)

```

```{r}
xgb_swiss_roll <- xgb.DMatrix(data=as.matrix(swiss_roll[index,1:3]),label=as.numeric(swiss_roll$class[index])-1)
swiss_roll_num_class <- length(levels(swiss_roll$class))
xgb_fit <- xgboost(data = xgb_swiss_roll, 
eta = 0.5,
max_depth = 10, 
nround=25, 
subsample = 0.7,
colsample_bytree = 0.7,
objective = "binary:logistic",
verbose = 0
)
label <- predict(xgb_fit,as.matrix(swiss_roll[-index,1:3])) 
```


## find good N

### n = 400, N = 40

```{r}
weight_index_swiss_roll <- rep(NA,1000)
for(i in 1:1000){
  weight_index_swiss_roll[i] <- weight_index(swiss_roll[-index,1:3],label,N = 40)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 400, N = 200

```{r}
weight_index_swiss_roll <- rep(NA,1000)
for(i in 1:1000){
  weight_index_swiss_roll[i] <- weight_index(swiss_roll[-index,1:3],label,N = 200)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 400, N = 400

```{r}
weight_index_swiss_roll <- rep(NA,1000)
for(i in 1:1000){
  weight_index_swiss_roll[i] <- weight_index(swiss_roll[-index,1:3],label,N = 400)$allproportion
}
plot(density(weight_index_fashion_mnist))
```

### n = 400, N = 800

```{r}
weight_index_swiss_roll <- rep(NA,1000)
for(i in 1:1000){
  weight_index_swiss_roll[i] <- weight_index(swiss_roll[-index,1:3],label,N = 800)$allproportion
}
plot(density(weight_index_fashion_mnist))
```



## find good weight

目前指標

```{r}
(swiss_roll_index <- weight_index(swiss_roll[-index,1:3],label,N = 800)$allproportion)
```


### index = 8 

```{r}
w <- weight_by_index(swiss_roll_index,8,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```


### index = 5 

```{r}
w <- weight_by_index(swiss_roll_index,5,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```

### index = 2 

```{r}
w <- weight_by_index(swiss_roll_index,2,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```

### index = 1 

```{r}
w <- weight_by_index(swiss_roll_index,1,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```

### index = 0.5 

```{r}
w <- weight_by_index(swiss_roll_index,0.5,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```

### index = 0.25 

```{r}
w <- weight_by_index(swiss_roll_index,0.25,swiss_roll[-index,1:3],label)
set.seed(610811101)
swiss_roll_tsne_2 <- cbind(swiss_roll[-index,1:3],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(swiss_roll$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(swiss_roll_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="swiss_roll") 
```


# mlbench.spirals

```{r}
mlbench.spirals <- mlbench::mlbench.spirals(500,cycles = 3,sd = 0.04)
spirals <- cbind(mlbench.spirals$x,mlbench.spirals$classes) %>%
  as.data.frame() %>%
  `names<-`(c("x","y","class"))

index <- sample(1:nrow(spirals),0.6*nrow(spirals))

hchart(spirals,"scatter",hcaes(x = x,y=y,group = class))
```

```{r}
xgb_spirals <- xgb.DMatrix(data=as.matrix(spirals[index,1:2]),label=as.numeric(spirals$class[index])-1)
spirals_num_class <- length(levels(spirals$class))
xgb_fit <- xgboost(data = xgb_spirals, 
eta = 0.5,
max_depth = 10, 
nround=25, 
subsample = 0.7,
colsample_bytree = 0.7,
objective = "binary:logistic",
verbose = 0
)
label <- predict(xgb_fit,as.matrix(spirals[-index,1:2])) 
```

## find good N

### n = 200, N = 20

```{r}
weight_index_spirals <- rep(NA,1000)
for(i in 1:1000){
  weight_index_spirals[i] <- weight_index(spirals[-index,1:2],label,N = 20)$allproportion
}
plot(density(weight_index_spirals))
```


### n = 200, N = 100

```{r}
weight_index_spirals <- rep(NA,1000)
for(i in 1:1000){
  weight_index_spirals[i] <- weight_index(spirals[-index,1:2],label,N = 100)$allproportion
}
plot(density(weight_index_spirals))
```

### n = 200, N = 200

```{r}
weight_index_spirals <- rep(NA,1000)
for(i in 1:1000){
  weight_index_spirals[i] <- weight_index(spirals[-index,1:2],label,N = 200)$allproportion
}
plot(density(weight_index_spirals))
```

### n = 200, N = 400

```{r}
weight_index_spirals <- rep(NA,1000)
for(i in 1:1000){
  weight_index_spirals[i] <- weight_index(spirals[-index,1:2],label,N = 400)$allproportion
}
plot(density(weight_index_spirals))
```

## find good weight

目前指標

```{r}
(spirals_index <- weight_index(spirals[-index,1:2],label,N = 400)$allproportion)
```


### index = 8 

```{r}
w <- weight_by_index(spirals_index,8,spirals[-index,1:2],label)
set.seed(610811101)
spirals_tsne_2 <- cbind(spirals[-index,1:2],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(spirals$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(spirals_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="spirals") 
```

### index = 5 

```{r}
w <- weight_by_index(spirals_index,5,spirals[-index,1:2],label)
set.seed(610811101)
spirals_tsne_2 <- cbind(spirals[-index,1:2],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(spirals$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(spirals_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="spirals") 
```

### index = 2 

```{r}
w <- weight_by_index(spirals_index,2,spirals[-index,1:2],label)
set.seed(610811101)
spirals_tsne_2 <- cbind(spirals[-index,1:2],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(spirals$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(spirals_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="spirals") 
```

### index = 1 

```{r}
w <- weight_by_index(spirals_index,1,spirals[-index,1:2],label)
set.seed(610811101)
spirals_tsne_2 <- cbind(spirals[-index,1:2],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(spirals$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(spirals_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="spirals") 
```

### index = 0.5 

```{r}
w <- weight_by_index(spirals_index,0.5,spirals[-index,1:2],label)
set.seed(610811101)
spirals_tsne_2 <- cbind(spirals[-index,1:2],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(spirals$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(spirals_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="spirals") 
```

### index = 0.25 

```{r}
w <- weight_by_index(spirals_index,0.25,spirals[-index,1:2],label)
set.seed(610811101)
spirals_tsne_2 <- cbind(spirals[-index,1:2],label) %>% 
  wtsne(check_duplicates = F,pca = F,col_weights = w) %$% 
  Y %>% 
  as.data.frame() %>% 
  cbind(spirals$class[-index]) %>% 
  `names<-`(c("x","y","group"))

hchart(spirals_tsne_2,"scatter", hcaes(x=x,y=y,group = group)) %>%
  hc_title(text ="spirals") 
```